Selecting and Controlling Physical Devices Through a Head-Mounted Display with Infrared Targeting

### 2013-09-02 doc/sigchi14/introduction.tex
pass over related work and device section

In this paper, we introduce a novel method for selecting and controlling smart appliances in physical spaces though the use of a head-worn computing device with near-eye display and wireless communication. We augment Google Glass\footnote{\url{http://www.google.com/glass/start/}} with custom hardware for this purpose. Users first look in the direction of the device they wish to control to acquire it (e.g., at a lamp for controlling lighting, or at a speaker to change music playback volume). If multiple devices fall within communication range, an on-screen disambiguation dialog lets users select a single target. Once acquired, a device specific control UI enables adjustment of discrete and continuous parameters through a touchpad interface (see Figure~\ref{fig:teaser}).

Our hardware relies on infrared communication between Glass and target devices to establish a connection; and on wireless ZigBee radio communication to exchange control messages.  Target devices similarly have IR receivers and ZigBee radios. These choices offer selection-through-head-orientation to initiate interaction; once initiated, users do not have to look at the target device for control commands.

>>>>

In this paper, we introduce a novel method for selecting and controlling smart appliances in physical spaces though the use of a head-worn computing device with near-eye display and wireless communication. We augment Google Glass\footnote{\url{http://www.google.com/glass/start/}} with custom hardware for this purpose. Users first look in the direction of the device they wish to control to initiate interaction (e.g., at a lamp to control lighting, or at a speaker to change music playback volume). If multiple devices fall within communication range, an on-screen disambiguation dialog lets users select a single target. Once acquired, a device specific control UI shown on the head-mounted display enables adjustment of discrete and continuous parameters through a touchpad interface (see Figure~\ref{fig:teaser}).

Our hardware relies on infrared communication between Glass and target devices to establish a connection; and on wireless ZigBee radio communication to exchange control messages.  Glass is augmented with a narrow IR emitter and a ZigBee ratio. Target devices similarly have IR receivers and ZigBee radios. These choices offer selection-through-head-orientation to initiate interaction; once initiated, users can look away from the target device while issuing control commands.
